Parsing Postfix log files

### 2007-07-09 doc/logparser.tex
populate-rules.sql: Make the tracking rule provide defaults for {server,client}_{hostname,ip} to handle forwarded bounce notifications. logparser.tex: Updated to match changes.  May need a little more added, dunno yet. Parser.pm: * Timeout for discarding cleanup lines increased to 10 minutes. * Added cloned_by * Tidy up the smtpd and last cloned mail using tidy_after_timeout() whenever there's a timeout, smtpd dies, is killed, or watchdog triggers - if the pid still exists (sometimes it doesn't, dunno why, not too bothered).  Missing cloned mail won't be committed now, reducing warnings. Also

    \item The mail will not have been tagged as a tracked mail (see
        section~\ref{tracking-re-injected-mail}).

@@

    \item The timestamp of the cleanup line must be within seven minutes of
        the mail acceptance timestamp.  Timeouts happen after five minutes,
        but some data may have been transferred slowly, and empirical
        evidence suggests seven minutes is a good compromise between false
        positives and false negatives.

@@

Occasionally an smtpd will just stop logging, without any explicit reason.
After poring over logs for some time there are several reasons for this
infrequent occurrence:

@@

The above appear to cover all situations where an smtpd suddenly stops
logging.

>>>>

@@

    \item The timestamp of the cleanup line must be within ten minutes of
        the mail acceptance timestamp.  Timeouts happen after five minutes,
        but some data may have been transferred slowly, and empirical
        evidence shows that ten minutes is not unreasonable; hopefully it
        is a good compromise between false positives and false negatives.

@@

Occasionally an smtpd will just stop logging, without an immediately
obvious reason.  After poring over logs for some time there are several
reasons for this infrequent occurrence:

@@

The above appear to cover all situations where an smtpd suddenly stops
logging.  In addition to removing an active connection the last accepted
mail may need to be discarded, as detailed in
section~\ref{timeouts-during-data-phase}.
